---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tastypie

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/tastypie)](https://CRAN.R-project.org/package=tastypie)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

You only need to type "why pie charts are bad" on Google to find thousands of articles full of (very valid) reasons why this type of chart should not be used.  
**However**, my mother, a high school teacher of Latin and Italian literature, swears she understands more from something like this:

```{r,include=FALSE}
df <- data.frame(
  group = c("My mum", "Is", "Strange?"),
  value = c(20, 30, 50)
)
head(df)
library(ggplot2)
library(knitr)
```

```{r}
pie<- ggplot(df, aes(x="", y=value, fill=group))+
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y", start=0) # to be replaced by a function from the package
pie
```

than from something like this:

```{r}
kable(df)
```

Now, I love my mum, and I want her to be happy. And maybe there are other people in the world in this *situation*, so, why not helping?  
  
Easy pie charts!  
Just a wrapper for [ggplot2](https://ggplot2.tidyverse.org/) functions for making pie charts in an easier way.

## Installation

You can install the released version of tastypie from [CRAN](https://CRAN.R-project.org) with:

``` {r, eval = FALSE}
install.packages("tastypie")
```


And the development version from [GitHub](https://github.com/) with:

``` {r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("PaoloDalena/tastypie")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval = FALSE}
library(tastypie)
## basic example code
```

