---
title: "available_templates"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{available_templates}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  dpi = 50
)
```

## Available templates for **`pie_bake()`**

Here you can find a comprehensive visualization of all the possible templates that you can access using **`pie_bake()`**.  
A fairly simple data frame with 5 groups will be considered. Percentages will be displayed (i.e. the argument `perc` will be fixed to `TRUE`), with the title corresponding to the template name and a generic group name (i.e. "groups").

*The same for the* **`pie_bake_pro()`** *function can be found by scrolling down.*

```{r,fig.align = "center", out.width="75%", out.height="75%"}
library(tastypie)
ex <- data.frame(
  LETTERS[1:5],
  c(65, 24, 54, 12, 43)
)

for(i in pie_template_list){
  print(pie_bake(ex, template = i, perc = TRUE, title = i))
}
```


## Available templates for **`pie_bake_pro()`**

Here we don't have to set the argument `perc` (there are some templates that display percentages anyways).

```{r, fig.align = "center", out.width="75%", out.height="75%"}
ex <- data.frame(
  LETTERS[1:5],
  c(65, 24, 54, 12, 43)
)

for(i in pie_template_list_pro){
  print(pie_bake_pro(ex, template = i, title = i))
}
```

## Available templates for **`bubble_blow()`**

Below you can see the different templates available for the function **`bubble_blow()`** that allows the user to easily create cool circular packing charts.  
  

A fairly simple data frame with 10 groups will be considered. Percentages will be displayed below the group labels (i.e. the argument `perc` will be fixed to `below`), with the title corresponding to the template name.


```{r, fig.align = "center", out.width="75%", out.height="75%"}
exblow <- data.frame(
  LETTERS[1:8],
  c(33, 24, 54, 12, 43, 88, 66, 78)
)

available_templates_bub <- c("bub1", "bub2", "bub3", "bub4", "bub5")

for(i in available_templates_bub){
  print(bubble_blow(exblow, template = i, perc = "below", title = i))
}
```
